CSCI 580 : Monte Carlo Path Tracing

### 2015-11-25 paper/paper.tex
sketch paper outline

\section{Abstract}
This will depend on our results.

@@

\section{Prior Work}
The origins of path tracing begin with ray tracing, first outlined in A. Appel's 1968 paper[1]. In the ray tracing technique, rays are cast out from the camera, or eye, through the image plane, and into the scene. The first surface it collides with is the one rendered for that pixel. Additionally, rays called shadow rays are cast from the light sources and determine whether or not the surface is being occluded by another, which would be collided with first by the shadow ray.\\

A further development was Whitted ray tracing[2], wherein rays generate new rays upon collision with a surface, for direct illumination, perfect refraction and perfect reflection.

>>>>

\section{Abstract}
This will depend on our results.\\
I predict this paper to be around 4 pages since it's in a rather condensed format.

@@

\section{Prior Work}
The origins of path tracing begin with ray tracing, first outlined in A. Appel's 1968 paper[1]. In the ray tracing technique, rays are cast out from the camera, or eye, through the image plane, and into the scene. The first surface it collides with is the one rendered for that pixel. Additionally, rays called shadow rays are cast from the light sources and determine whether or not the surface is being occluded by another, which would be collided with first by the shadow ray.A further development was Whitted ray tracing[2], wherein rays generate new rays upon collision with a surface, for direct illumination, perfect refraction and perfect reflection.\\

MONTE CARLO PAPERS

\section{The Monte Carlo Path Tracing Algorithm}
explain the algorithmia

\section{Implementation}
Explain architectural changes.
Explain what parts of Monte Carlo we did.

\section{Results}
Pictures, maybe some figures for different numbers of rays.

% SAMPLE BIBLIO

SAMPLE BIBLIOGRAPHY

\begin{thebibliography}{4}

\bibitem{Pottinger}
Pottinger, D.C. 2005 Terrain Analysis in Realtime Strategy Games, \emph{Ensemble Studios}.
\\
\bibitem{Johan}
Hagelb\"ack, J., and Johansson, S. J. 2008. Using multiagent
potential fields in real-time strategy games. In
Padgham, L., and Parkes, D., eds., \emph{Proceedings of the Seventh
International Conference on Autonomous Agents and
Multi-agent Systems (AAMAS)}.
\\
\bibitem{Thurau}
Thurau, C., and Bauckhage C. 2004. Learning human-like Movement Behavior for
Computer Games. \emph{Gerhard Sagerer Applied Computer Science,
Bielefeld University}.
\\
\bibitem{Johan_2}
Hagelb\"ack, J., and Johansson, S. J. 2008. The Rise of Potential Fields in Real Time Strategy Bots. In \emph{ Proceedings of the 4th Conference on Artificial Intelligence and Interactive Digital Entertainment (AIIDE)}.
\end{thebibliography}
